The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-29 paper/paper.tex
paper: use section labels

\subsection{Defining frames and specifying frame restrictions}

@@

\subsection{Defining paintings}

@@

\subsection{Defining frame restrictions and specifying frame coherence laws}

@@

\subsection{Defining painting restrictions}

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohptype[n][\lbrack 0,p-1 \rbrack] & \fulldepscohs[n] & :      & \U                                                           \\
    \cohptype[n]                        & \unitpoint       & \defeq & \unittype                                                    \\
    \cohptype[n][\lbrack 0,p \rbrack]   & \fulldepscohs[n] & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                        &                  &        & \left\{
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                                       \\
      \Pi d:\framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])). \\
      \restrp[n][p][q][\epsilon](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][r][\omega]
      (\fulldepscohs[n])(d)(c)) =_{\cohf[n][p][q][r][\epsilon][\omega]}                                                                               \\
      \restrp[n][p][r][\omega](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][q+1][\epsilon]
      (\fulldepscohs[n])(d)(c))
    \end{array}
    \right.                                                                                                                        \\
  \end{array}
\end{equation*}
where we use the ``equality over'' notation $t =_e u$ to mean $\overrightarrow{e}(t) = u$ whenever $t$ is of some type $P(a)$, $u$ of type $P(b)$ and $e$ a proof of $a = b$.
\subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws}

@@

\subsection{Defining painting coherence laws}

@@

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$ (where $\deps[n][\lbrack 0,n \rbrack]$ come from the assumptions at level $n$) and to build the following:
\begin{itemize}
  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$.
  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack](E)$.
  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
  \item we define $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
  \item we define $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
\end{itemize}

>>>>

\subsection{Defining frames and specifying frame restrictions\label{sec:mkframe}}

@@

\subsection{Defining paintings\label{sec:mkpainting}}

@@

\subsection{Defining frame restrictions and specifying frame coherence laws\label{sec:mkrestrf}}

@@

\subsection{Defining painting restrictions\label{sec:mkrestrp}}

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohptype[n][\lbrack 0,p-1 \rbrack] & \fulldepscohs[n] & :      & \U                                                           \\
    \cohptype[n]                        & \unitpoint       & \defeq & \unittype                                                    \\
    \cohptype[n][\lbrack 0,p \rbrack]   & \fulldepscohs[n] & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                        &                  &        & \left\{
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                                       \\
      \Pi d:\framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])). \\
      \restrp[n][p][q][\epsilon](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][r][\omega]
      (\fulldepscohs[n])(d)(c)) =_{\cohf[n][p][q][r][\epsilon][\omega]}                                                                               \\
      \restrp[n][p][r][\omega](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][q+1][\epsilon]
      (\fulldepscohs[n])(d)(c))
    \end{array}
    \right.                                                                                                                        \\
  \end{array}
\end{equation*}
where we use the ``equality over'' notation $t =_e u$ to mean $\overrightarrow{e}(t) = u$ whenever $t$ is of some type $P(a)$, $u$ of type $P(b)$ and $e$ a proof of $a = b$.
\subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws\label{sec:mkcohf}}

@@

\subsection{Defining painting coherence laws\label{sec:mkcohp}}

@@

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$ (where $\deps[n][\lbrack 0,n \rbrack]$ come from the assumptions at level $n$) and to build the following:
\begin{itemize}
  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$ (section~\ref{sec:mkframe}).
  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$ (section~\ref{sec:mkpainting}).
  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack](E)$ (section~\ref{sec:mkrestrf}).
  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$ (section~\ref{sec:mkrestrp}).
  \item we define $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ (section~\ref{sec:mkcohf}).
  \item we define $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$ (section~\ref{sec:mkcohp}).
\end{itemize}
